%------------------------------------------------------------------------------
% CV in Latex
% Author : Charles Rambo
% Based off of: https://github.com/sb2nov/resume and Jake's Resume on Overleaf
% Most recently updated version may be found at https://github.com/fizixmastr 
% License : MIT
%------------------------------------------------------------------------------

\documentclass[11pt]{article}
%a4paper
%\documentclass[letterpaper,11pt]{article} %For use in US
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    }
\usepackage[english]{babel}
\usepackage{tabularx}

\begin{comment}
I am by no means a professional when it comes to the CV's/resumes, I have
received various trainings on how to write a CV and resume from my high 
school, as well as the Austin College and University of Eastern Finland's
career counseling departments. As I intend to share my CV as a template, I 
feel that it is my responsibility to provide explanations of my work.
\end{comment}


%-----FONT OPTIONS-------------------------------------------------------------
\begin{comment}
The font of the document will impact not just how readable it is, but how it is
perceived. In the "The Craft of Scientific Writing" by Michael Alley, shares a
common fonts for publication as well as their use. I have chosen to use
Palatino for its legibility, some others are given below. There is far too much
about typography to discus here. Note: serif fonts have short projecting
strokes, sans-serif fonts are sans (without) these strokes.
\end{comment}


% serif
% \usepackage{palatino}
% \usepackage{times} %This is the default as well
% \usepackage{charter}

% sans-serif
% \usepackage{helvet}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

%-----PAGE SETUP---------------------------------------------------------------

% Adjust margins
\addtolength{\oddsidemargin}{-1cm}
\addtolength{\evensidemargin}{-1cm}
\addtolength{\textwidth}{2cm}
\addtolength{\topmargin}{-1cm}
\addtolength{\textheight}{2cm}

% Margins for US Letter size
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
%\addtolength{\topmargin}{-.5in}
%\addtolength{\textheight}{1.0in}

\urlstyle{tt}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0cm}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


%-----CUSTOM COMMANDS FOR FORMATTING SECTIONS----------------------------------
\newcommand{\CVItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\CVSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\CVSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \text{\small#1} & \text{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\CVSubItem}[1]{\CVItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\CVSubHeadingListStart}{\begin{itemize}[leftmargin=0.5cm, label={}]}
% \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} % Uncomment for US
\newcommand{\CVSubHeadingListEnd}{\end{itemize}}
\newcommand{\CVItemListStart}{\begin{itemize}}
\newcommand{\CVItemListEnd}{\end{itemize}\vspace{-5pt}}

%------------------------------------------------------------------------------
% CV STARTS HERE  %
%------------------------------------------------------------------------------
\begin{document}

%-----HEADING------------------------------------------------------------------

\begin{center}
    \textbf{\Large \textbf{MARTIN HABETS}} \\ \vspace{2pt} %\scshape sets small capital letters, remove if desired
    \href{mailto:martin.habets@eui.eu}{martin.habets@eui.eu} \
\end{center}



\begin{comment}
This CV was written for specifically for positions I was applying for in
academia, and then modified to be a template.

A standard CV is about two pages long where as a resume in the US is one page.
sections can be added and removed here with this in mind. In my experience, 
education, and applicable work experience and skills are the most import things
to include on a resume. For a CV the Europass CV suggests the categories: Work
Experience, Education and Training, Language Skills, Digital Skills,
Communication and Interpersonal Skills, Conferences and Seminars, Creative Works
Driver's License, Hobbies and Interests, Honors and Awards, Management and
Leadership Skills, Networks and Memberships, Organizational Skills, Projects,
Publications, Recommendations, Social and Political Activities, Volunteering.

Your goal is to convey a who, what , when, where, why for every item you share. 
The who is obviously you, but I believe the rest should be done in that order.
For example below. An employer cares most about the degree held and typically 
less about the institution or where it is located (This is still good 
information though). Whatever order you choose be consistent throughout.
\end{comment}

%-----RESEARCH INTERESTS----------------------------------------------------

\section{Research Interests}
 \begin{itemize}[leftmargin=0.5cm, label={}]
    \small{\item{
     \textbf{Primary Field: }{Environmental Economics} \\
     \textbf{Interests: }{Applied Micro, Gender, Development} 
    }}
 \end{itemize}


  %-----WORK IN PROGRESS----------------------------------------------------

\section{Work in Progress}
 \begin{itemize}[leftmargin=0.5cm, label={}]
    \small{\item{
	Temperature Variation and Domestic Violence\\
	\vspace{.2cm}
	Role of Siblings in Gender Norms Formation (with Libertad González)
	%	\vspace{.2cm}
	%The Effect of Sibling Gender on Attitude (with J reuter)
    }}
 \end{itemize}
 


%-----EDUCATION----------------------------------------------------------------
\section{Education}
  \CVSubHeadingListStart
%    \CVSubheading % Example
%      {Degree Achieved}{Years of Study}
%      {Institution of Study}{Where it is located}
    \CVSubheading
      {{PhD in Economics $|$ \emph{\small{European University Institute (Florence)}}}}{2020 -- Present}
      {Advisors: Alessandro Tarozzi and Thomas Crossley}{}
    \CVSubheading
      {{Master in Economics $|$ \emph{\small{College of Europe (Bruges)}}}}{2018 -- 2019}
      {Research project with Andrés Rodríguez-Pose}{}
    \CVSubheading
      {{Bachelor and Master in Economics $|$ \emph{\small{University of Liege (Belgium)}}}}{2013 -- 2018}
      {Exchanges in Seoul and Bogota}{}
  \CVSubHeadingListEnd
  

 
%-----TEACHING EXPERIENCE----------------------------------------------------

\section{Teaching Experience}
  \CVSubHeadingListStart
     \CVSubheading
      {{Theory and Practice of Causal Inference}}{Fall 2023}
      {EUI, PhD level $|$ Teaching Assistant to Fabrizia Mealli} {}
    \CVSubheading
      {{Topics in Microeconometrics}}{Spring 2023 \& 2024}
      {EUI, PhD level $|$ Teaching Assistant to Alessandro Tarozzi} {}
  \CVSubHeadingListEnd


%-----WORK EXPERIENCE----------------------------------------------------------

\section{Work Experience}
  \CVSubHeadingListStart
%    \CVSubheading %Example
%      {What you did}{When you worked there}
%      {Who you worked for}{Where they are located}
%      \CVItemListStart
%        \CVItem{Why it is important to this employer}
%      \CVItemListEnd
    \CVSubheading
      {European Commission, Brussels}{Oct 2019 -- Mar 2020}
      {Blue Book trainee at DG ECFIN}{}
    \CVSubheading
      {Belgian Ministry of Finances, Brussels, Belgium}{Apr 2018 - Jun 2018}
      {Intern at the Treasury}{}
    \CVSubheading
      {Embassy of Belgium, Santiago, Chile}{Jan 2017 -- Feb 2017}
      {Intern}{}
  \CVSubHeadingListEnd

%-----CONFERENCES AND PRESENTATIONS--------------------------------------------

%\section{Conferences and Presentations}
%  \CVSubHeadingListStart
%%    \CVSubheading % Example
%%      {Work Presented}{When}
%%      {Occasion}{}
%    \CVSubheading
%      {Photometric Filter Fidelity and Use for Be Star Identification}{November 2017}
%      {Austin College Physics Research Seminar}{}
%  \CVSubHeadingListEnd


%-----AWARDS AND GRANTS-------------------------------------------------------------------

\section{Grants and Awards}
 \begin{itemize}[leftmargin=0.5cm, label={}]
    \small{\item{
EUI fourth year grant \\
 F.R.S.-FNRS EUI Doctoral Grant\\
Full scholarship awarded by Ageas for the College of Europe\\
Erasmus+ Grant for visiting Universidad Nacional de Colombia (Bogota) \\
Erasmus+ Grant for visiting Kyung Hee University (Seoul)
    }}
 \end{itemize}

%-----SKILLS-------------------------------------------------------------------

\section{Skills}
 \begin{itemize}[leftmargin=0.5cm, label={}]
    \small{\item{
     \textbf{Languages}{: French (Native), English (fluent), Spanish (fluent), Italian, Dutch, German (intermediate)} \\
     \textbf{Programming}{: R, Stata, Python} \\
     \textbf{Document Creation}{: Quarto, LaTeX} 
    }}
 \end{itemize}
    
%-----REFERENCES-------------------------------------------------------------------

\section{References}
 \begin{itemize}[leftmargin=0.5cm, label={}]
    \small{\item{
     \textbf{Alessandro Tarozzi: }{: European University Institute  $|$ \href{mailto:alessandro.tarozzi@upf.edu}{alessandro.tarozzi@upf.edu}} \\
     \textbf{Thomas Crossley}{:  University of Michigan $|$ \href{mailto:tfcross@umich.edu}{tfcross@umich.edu}} 
    }}
 \end{itemize} 
    
  
%------------------------------------------------------------------------------
\end{document}